### 2018-07-07 Proposals/NERC-CCUS_2015/Outline_ReactiveCCS.tex

\begin{enumerate}[(a)]
%
\item {\bf University of Aberdeen (UoA), School of Engineering - Environmental and Industrial Fluid Mechanics Group (EnIFluG)\footnote{\href{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}}:} The Group specialises in combined computational methods, laboratory experimentation, and field work on permeable/porous media flows, sediment transport, coastal monitoring, turbulent buoyant jets and large-scale environmental flows. The Group has outstanding experimental facilities, including a range of large water. The latest addition is the petroleum engineering laboratory which represents a \pounds 200k investment in new equipment. The laboratory comprises four independent core-flood rigs with custom-made Hassler cells, an Anton Paar density meter and glass capillary viscometers with thermal bath. In May, UoA was awarded a further \pounds 950k (under the framework of Oil $\&$ Gas Academy of Scotland) for the purchase of equipment related to O$\&$G training. Among the equipment that will be purchased is an X-ray micro-computed tomography (microCT) system for in-situ imaging of fluids in rock samples. \red{make it more general}. \\
{\bf Dr Jefferson Gomes (JG)} leads the development of the computational multi-physics models within Fluidity. He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.

%
\item {\bf Imperial College London (IC), Department of Earth Science and Engineering – Applied Modelling and Computation Group (AMCG)\footnote{\href{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}}:} The Group is is a multi-disciplinary team of 60 scientists and engineers with backgrounds in engineering, mathematics, physics, earth and computational sciences. It specialises in the development of world-class numerical methods for modelling multi-scale multi-physical processes, with application to fracture and fragmentation, porous media and turbulent flows, nuclear criticality safety, industrial and environmental flows, ocean modelling, impact cratering and air pollution. \\
{\bf Prof. Christopher C. Pain (CCP)} is head of AMCG. He has a diverse range of modelling/physics interests including: general CFD (which comprises multiphase flow and geophysical fluid dynamics), nuclear safety, optimisation, numerical research (including parallel solution techniques, error measures and mesh adaptivity) and discretisation techniques10-14. He is the original author of the general-purpose parallel CFD model Fluidity, with mesh adaptivity, multiphase and ocean modelling features and has published 125 journal papers and graduated 33 PhD students. 
%
\end{enumerate}

@@

The main objectives of this proposal are:
\begin{enumerate}[(i)]
%
   \item Investigation of \CO\; plume dynamics (migration and leakage);
%
   \item \red{Investigation of multi-fluid flows through zones of potential rheological weakness in the overburden (e.g., faults and chimneys): solid-fluid interactions and stress-induced fractures formation;}
%
   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
%
   \item Model quality assurance
%
\end{enumerate}

>>>>

%\begin{enumerate}[(a)]
%
%\item 
{\bf University of Aberdeen (UoA), School of Engineering - Environmental and Industrial Fluid Mechanics Group (EnIFluG)\footnote{\href{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}{http://www.abdn.ac.uk/engineering/research/environmental-industrial-fluid-mechanics-122.php}}:} The Group specialises in combined computational methods, laboratory experimentation, and field work on permeable/porous media flows, sediment transport, coastal monitoring, turbulent buoyant jets and large-scale environmental flows. The Group has outstanding experimental facilities, including a range of large water. The latest addition is the petroleum engineering laboratory which represents a \pounds 200k investment in new equipment. The laboratory comprises four independent core-flood rigs with custom-made Hassler cells, an Anton Paar density meter and glass capillary viscometers with thermal bath. In May, UoA was awarded a further \pounds 950k (under the framework of Oil $\&$ Gas Academy of Scotland) for the purchase of equipment related to O$\&$G training. Among the equipment that will be purchased is an X-ray micro-computed tomography (microCT) system for in-situ imaging of fluids in rock samples. \red{make it more general}. \\

\medskip
{\bf Dr Jefferson Gomes (JG)} leads the development of the computational multi-physics models within Fluidity. He published >25 journal papers on CFD, porous media flows, fluid phase equilibria, nuclear criticality and computational optimisation.\\

\medskip
{\bf Dr Yukie Tanino (YT)} research combines theory and laboratory experiment to model flow and mass transport in obstructed and/or confined systems, including geological reservoirs, inclined pipes, and artificial wetlands for wastewater treatment. She manages the recently established petroleum engineering laboratory in the School.\\

\medskip
{\bf Dr XXXXXX (XX)} ...

%
%\item {\bf Imperial College London (IC), Department of Earth Science and Engineering – Applied Modelling and Computation Group (AMCG)\footnote{\href{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}{http://www.imperial.ac.uk/engineering/departments/earth-science/research/research-groups/amcg}}:} The Group is is a multi-disciplinary team of 60 scientists and engineers with backgrounds in engineering, mathematics, physics, earth and computational sciences. It specialises in the development of world-class numerical methods for modelling multi-scale multi-physical processes, with application to fracture and fragmentation, porous media and turbulent flows, nuclear criticality safety, industrial and environmental flows, ocean modelling, impact cratering and air pollution. \\
%{\bf Prof. Christopher C. Pain (CCP)} is head of AMCG. He has a diverse range of modelling/physics interests including: general CFD (which comprises multiphase flow and geophysical fluid dynamics), nuclear safety, optimisation, numerical research (including parallel solution techniques, error measures and mesh adaptivity) and discretisation techniques10-14. He is the original author of the general-purpose parallel CFD model Fluidity, with mesh adaptivity, multiphase and ocean modelling features and has published 125 journal papers and graduated 33 PhD students. 
%
%\end{enumerate}

@@

The main objectives of this proposal are \red{(big picture here ...)}: 
\begin{enumerate}[(a)]
%
   \item Investigation of \CO\; plume dynamics (migration and leakage);
%
   \item \red{Investigation of multi-fluid flows through zones of potential rheological weakness in the overburden (e.g., faults and chimneys): solid-fluid interactions and stress-induced fractures formation;}
%
%   \item \red{Model uncertainty quantification: sensor network (data assimilation) and ROM};
%
   \item Model quality assurance (monitoring $\&$ verification for risk assessment and environmental impact).
%
\end{enumerate}

{\bf The novelty of this project is in addressing in an integrated way: detailed multiphase flow transport modelling under reservoir conditions (\CO plume migration $\&$ leakage); changes on petrophysical properties (permeability/porosity spatial- and time-variability); solid-fluid interactions (integrity of repositories); and monitoring $\&$ verification technologies.} \red{add here science question(s) we want to address and the relevance to both applications and the call itself!.}

\medskip
We shall consider two integrated length-scales in the CCUS problem: 
\begin{enumerate}[(a)]
  \item \red{flow mechanisms and structures in pore-scale} -- {\bf YT};
  \item flow detachment in field-scale \blue{(develop this as a backbone for phase change (multi-physics) and flow instability)} -- {\bf JG}.
\end{enumerate}

%%%
%%% SUBSECTION
%%%
\subsection{Programme and Methodology}

\begin{description}%[{WP.}1]
%
\item[WP-1 Investigation of \CO Plume Dynamics: Migration and in Porous Media:] \red{Topics that may be covered here - JG}
%
\begin{enumerate}[{WP-1.}1]
%
\item Extend current multi-component and multiphase model formulations for:
\begin{enumerate}
 \item parametrised chemical reactions and phase change to take into account `simple' precipitation, dissolution and exsolution processes;
 \item non-isothermal process
\end{enumerate}
%
\item Include time- and spatial-variability of porosity and permeability
%
\item Large-scale simulations (parallel)
%
\end{enumerate}

%
\item[WP-2 Monitoring $\&$ Verification for Risk Assessment and Environmental Impact] bla
%
\begin{enumerate}[{WP-2.}1]
%
\item Model and software quality assurance
%
\item \blue{anything here from lab ??}
%
\item \blue{Field validation?}
%
\end{enumerate}
%
\item[WP-3 YT] bla
%
\end{description}
